Glasgow Hackerspace CIC Articles of Association

### 2024-02-20 articles.tex
All sections are done

\subsection{Termination of membership}
\subsubsection{Membership is not transferable to anyone else.}
\subsubsection{Membership is terminated if:}
\begin{subindentpara}

    \item the member dies or ceases to exist;
    \item otherwise in accordance with the Articles;
    \item the member fails to pay the membership subscription for more than 3 months, and has not been granted an exemption by the Directors;
    \item the member notifies the Hackerspace, via any means on which a director may be reached (in writing, including by Electronic Means) that they wish to cease to be a member; in which case, the member ceases to be a member from the time when the notice is received;
    \item the member is expelled by way of a resolution passed by not less than two thirds of those present and voting at a general meeting, providing the following procedures have been observed: 
    \begin{subindentlist}
        \item at least 21 days notice of the intention to propose the resolution must be given to the member concerned, specifying the grounds for the proposed expulsion; or
        \item the member concerned will be entitled to be heard on the resolution at the general meeting at which the resolution is proposed
    \end{subindentlist}
    \item or;
    \item the Directors may temporarily suspend any member from access to the Hackerspace's resources, if the behaviour of that member is deemed by the Directors to be unacceptable to the Hackerspace. Suspension will continue until either the Directors reverse the suspension, or an expulsion resolution is heard. The suspended member has the right to propose an expulsion resolution. A member expelled by such a resolution will nevertheless remain liable to pay to the Company any subscription or other sum owed by that member.
\end{subindentpara}
\subsubsection{Upon ceasing to be a member, all means of access to the Hackerspace, including but not limited to keys and access tokens, must be returned to the Hackerspace.}

@@

>>>>

\subsection{Termination of membership}
\subsubsection{Membership is not transferable to anyone else.}
\subsubsection{Membership is terminated if:}
\begin{subindentpara}
    \item the member dies or ceases to exist;
    \item otherwise in accordance with the Articles;
    \item the member fails to pay the membership subscription for more than 3 months, and has not been granted an exemption by the Directors;
    \item the member notifies the Hackerspace, via any means on which a director may be reached (in writing, including by Electronic Means) that they wish to cease to be a member; in which case, the member ceases to be a member from the time when the notice is received;
    \item the member is expelled by way of a resolution passed by not less than two thirds of those present and voting at a general meeting, providing the following procedures have been observed: 
    \begin{subindentpara} % Note initial indentation of this child indented paragraph section may go too far. Largely unimportant, but note it inherits absolute indentation of regular hanging paragraphs from the margin.
        \item at least 21 days notice of the intention to propose the resolution must be given to the member concerned,  specifying the grounds for the proposed expulsion; or
        \item the member concerned will be entitled to be heard on the resolution at the general meeting at which the resolution is proposed
    \end{subindentpara}
    \item or;
    \item the Directors may temporarily suspend any member from access to the Hackerspace's resources, if the behaviour of that member is deemed by the Directors to be unacceptable to the Hackerspace. Suspension will continue until either the Directors reverse the suspension, or an expulsion resolution is heard. The suspended member has the right to propose an expulsion resolution. A member expelled by such a resolution will nevertheless remain liable to pay to the Company any subscription or other sum owed by that member.
\end{subindentpara}
\subsubsection{Upon ceasing to be a member, all means of access to the Hackerspace, including but not limited to keys and access tokens, must be returned to the Hackerspace.}

@@

\subsection{Content of proxy notices}
\subsubsection{Proxies may only validly be appointed by a notice in writing (a “Proxy Notice”) which:}
\begin{subindentlist}
    \item [(a)] states the name of the member appointing the proxy;
    \item [(b)] identifies the person appointed to be that member’s proxy and the general meeting in relation to which that person is appointed;
    \item [(c)] is signed by or on behalf of the member appointing the proxy, or is authenticated in such manner as the directors may determine; and
    \item [(d)] is delivered to the Company in accordance with the Articles and any instructions contained in the notice of the general meeting to which they relate.
\end{subindentlist}
\subsubsection{The Company may require Proxy Notices to be delivered in a particular form, and may specify different forms for different purposes.}
\subsubsection{Proxy Notices may specify how the proxy appointed under them is to vote (or that the proxy is to abstain from voting) on one or more resolutions.}
\subsubsection{Unless a Proxy Notice indicates otherwise, it must be treated as:}
\begin{subindentlist}
    \item [(a)] allowing the person appointed under it as a proxy discretion as to how to vote on any ancillary or procedural resolutions put to the meeting; and
    \item [(b)] appointing that person as a proxy in relation to any adjournment of the general meeting to which it relates as well as the meeting itself.
\end{subindentlist}

\subsection{Delivery of proxy notices}
\subsubsection{A person who is entitled to attend, speak or vote (either on a show of hands or on a poll) at a general meeting remains so entitled in respect of that meeting or any adjournment of it, even though a valid Proxy Notice has been delivered to the Company by or on behalf of that person.}
\subsubsection{An appointment under a Proxy Notice may be revoked by delivering to the Company a notice in Writing given by or on behalf of the person by whom or on whose behalf the Proxy Notice was given.}
\subsubsection{A notice revoking the appointment of a proxy only takes effect if it is delivered before the start of the meeting or adjourned meeting to which it relates.}

\subsection{Amendments to resolutions}
\subsubsection{An ordinary resolution to be proposed at a general meeting may be amended by ordinary resolution if:}
\begin{subindentpara}
    \item notice of the proposed amendment is given to the Company in Writing by a person entitled to vote at the general meeting at which it is to be proposed not less than 48 hours before the meeting is to take place (or such later time as the chair of the meeting may determine); and
    \item the proposed amendment does not, in the reasonable opinion of the chair of the meeting, materially alter the scope of the resolution.
\end{subindentpara}
\subsubsection{A special resolution to be proposed at a general meeting may be amended by ordinary resolution, if:}
\begin{subindentpara}
    \item the chair of the meeting proposes the amendment at the general meeting at which the resolution is to be proposed; and
    \item the amendment does not go beyond what is necessary to correct a grammatical or other non-substantive error in the resolution.
\end{subindentpara}
\subsubsection{If the chair of the meeting, acting in good faith, wrongly decides that an amendment to a resolution is out of order, the chair’s error does not invalidate the vote on that resolution.}

\section*{Written Resolutions}
\subsection{\label{subsection:WrittenResolutions}Written resolutions}
\subsubsection{Subject to Article \ref{subsubsection:WrittenResolutionException}, a written resolution of the Company passed in accordance with this Article \ref{subsection:WrittenResolutions} shall have effect as if passed by the Company in general meeting:}
\begin{subindentpara}
    \item A written resolution is passed as an ordinary resolution if it is passed by a simple majority of the total voting rights of eligible members.
    \item A written resolution is passed as a special resolution if it is passed by members representing not less than 75\% of the total voting rights of eligible members. A written resolution is not a special resolution unless it states that it was proposed as a special resolution.
\end{subindentpara}
\subsubsection{In relation to a resolution proposed as a written resolution of the Company the eligible members are the members who would have been entitled to vote on the resolution on the circulation date of the resolution.}
\subsubsection{\label{subsubsection:WrittenResolutionException}A members’ resolution under the Companies Acts removing a Director before the expiration of their term of office may not be passed as a written resolution.}
\subsubsection{A copy of the written resolution must be sent to every member together with a statement informing the member how to signify their agreement to the resolution and the date by which the resolution must be passed if it is not to lapse. Communications in relation to written notices shall be sent to the Company’s auditors in accordance with the Companies Acts.}
\subsubsection{A member signifies their agreement to a proposed written resolution when the Company receives from them an authenticated Document identifying the resolution to which it relates and indicating their agreement to the resolution.}
\begin{subindentpara}
    \item If the Document is sent to the Company in Hard Copy Form, it is authenticated if it bears the member’s signature.
    \item If the Document is sent to the Company by Electronic Means, it is authenticated [if it bears the member’s signature] or [if the identity of the member is confirmed in a manner agreed by the Directors] or [if it is accompanied by a statement of the identity of the member and the Company has no reason to doubt the truth of that statement] or [if it is from an email Address notified by the member to the Company for the purposes of receiving Documents or information by Electronic Means].
\end{subindentpara}
\subsubsection{A written resolution is passed when the required majority of eligible members have signified their agreement to it.}
\subsubsection{A proposed written resolution lapses if it is not passed within 28 days beginning with the circulation date.}

\section*{Administrative Arrangements and Miscellaneous}
\subsection{Means of communication to be used}
\subsubsection{Subject to the Articles, anything sent or supplied by or to the Company under the Articles may be sent or supplied in any way in which the Companies Act 2006 provides for Documents or information which are authorised or required by any provision of that Act to be sent or supplied by or to the Company.}
\subsubsection{Subject to the Articles, any notice or Document to be sent or supplied to a Director in connection with the taking of decisions by Directors may also be sent or supplied by the means by which that Director has asked to be sent or supplied with such notices or Documents for the time being.}
\subsubsection{A Director may agree with the Company that notices or Documents sent to that Director in a particular way are to be deemed to have been received within an agreed time of their being sent, and for the agreed time to be less than 48 hours.}

\subsection{Irregularities}
\begin{subindentpara}
    \item The proceedings at any meeting or on the taking of any poll or the passing of a written resolution or the making of any decision shall not be invalidated by reason of any accidental informality or irregularity (including any accidental omission to give or any non-receipt of notice) or any want of qualification in any of the persons present or voting or by reason of any business being considered which is not referred to in the notice unless a provision of the Companies Acts specifies that such informality, irregularity or want of qualification shall invalidate it.
\end{subindentpara}

\subsection{Minutes}
\subsubsection{The Directors must cause minutes to be made in books kept for the purpose:}
\begin{subindentpara}
    \item of all appointments of officers made by the Directors;
    \item of all resolutions of the Company and of the Directors; and
    \item of all proceedings at meetings of the Company and of the Directors, and of committees of Directors, including the names of the Directors present at each such meeting;
    \item and any such minute, if purported to be signed (or in the case of minutes of Directors’ meetings signed or authenticated) by the chair of the meeting at which the proceedings were had, or by the chair of the next succeeding meeting, shall, as against any member or Director of the Company, be sufficient evidence of the proceedings.
\end{subindentpara}
\subsubsection{The minutes must be circulated to the members within 30 days of any appointments of officers; resolutions of the Company and of the Directors; and of any meetings of the Company and of the Directors, and of committees of Directors.}
\subsubsection{The minutes must be kept for at least ten years from the date of the meeting, resolution or decision.}

\subsection{Records and accounts}
\begin{subindentpara}
    \item The Directors shall comply with the requirements of the Companies Acts as to maintaining a members’ register, keeping financial records, the audit or examination of accounts and the preparation and transmission to the Registrar of Companies and the Regulator of:
\end{subindentpara}
\subsubsection{annual reports;}
\subsubsection{annual returns; and}
\subsubsection{annual statements of account.}

\subsection{Indemnity}
\subsubsection{Subject to Article \ref{subsubsection:IndemnityException}, a relevant Director of the Company or an associated company may be indemnified out of the Company’s assets against:}
\begin{subindentlist}
    \item [(a)] any liability incurred by that Director in connection with any negligence, default, breach of duty or breach of trust in relation to the Company or an associated company;
    \item [(b)] any other liability incurred by that Director as an officer of the Company or an associated company.
\end{subindentlist}
\subsubsection{\label{subsubsection:IndemnityException}This Article does not authorise any indemnity which would be prohibited or rendered void by any provision of the Companies Acts or by any other provision of law.}
\subsubsection{In this Article:}
\begin{subindentlist}
    \item [(a)] companies are associated if one is a subsidiary of the other or both are subsidiaries of the same body corporate; and
    \item [(b)] a “relevant Director” means any Director or former Director of the Company or an associated company.
\end{subindentlist}

\subsection{Insurance}
\subsubsection{The Directors may decide to purchase and maintain insurance, at the expense of the Company, for the benefit of any relevant Director in respect of any relevant loss.}
\subsubsection{In this Article:}
\begin{subindentlist}
    \item [(a)] a “relevant Director” means any Director or former Director of the Company or an associated company;
    \item [(b)] a “relevant loss” means any loss or liability which has been or may be incurred by a relevant Director in connection with that Director’s duties or powers in relation to the Company, any associated company or any pension fund or employees’ share scheme of the company or associated company; an
    \item [(c)] companies are associated if one is a subsidiary of the other or both are subsidiaries of the same body corporate.
\end{subindentlist}

\subsection{Changes to the articles}
\subsubsection{These articles may only be altered by special resolution of the members passed at a general meeting or by way of a special written resolution of the members.}

\subsection{Exclusion of model articles}
\begin{subindentpara}
    \item The relevant model articles for a company limited by guarantee are hereby expressly excluded.
\end{subindentpara}
